Symmetric Peer-to-Peer Applications

### 2022-09-04 tpd-22.tex
...

In this section, we evaluate if our design meets its goals to ensure that all
peers (a) meet event deadlines, (b) advance in sync in real time, and (c) can
leave and join the network and remain symmetric.
%
For each of these goals, we simulate different network scenarios varying the
(i) topology, (j) latency, (k) churn, and (k) frequency and (m) deadlines of
events.
For each scenario, we measure (x) the recurrence of time travels, (y) the
real-time pace of peers, and (z) the correctness of unstable peers, such that
they validate goals (a), (b), and (c), respectively.

@@

>>>>

In this section, we simulate an application varying the network topology,
latency, and churn, as well as the frequency and deadlines of events.
We use a single machine .
We then evaluate if our design meets its goals as follows:
%
\begin{enumerate}
\item \textbf{Event Deadlines:}
We measure the recurrence of time travels among peers.
If a peer experiences a time travel, it means that it received an event after
its deadline.
For instance, that would be the case when the source peer generates an event
with a small deadline in comparison to the latency to the farthest destination
peer.
More concretely, we teak the middleware implementation to count time travel
ticks.
We then measure the percentage of the sum of all time travels ticks over the to
the total simulation ticks (e.g., $1\%$, if all peers sum $1000$ time travel
ticks over $100k$ accumulated simulation ticks).
%
\item \textbf{Time Synchronization:}
We measure if peers advance in sync in real time using as a reference the peer
most advanced in time.
We start each peer with a random delay to force a time mismatch, and then
verify if they synchronize and remain synchronized during the whole simulation.
More concretely, we teak the middleware to .

More concretely, we measure the percentage o ticks diverging from the reference
peer (e.g., $1\%$, if .

converge

, and (c) can
Since peers run in different machines, their timelines will inevitably be out
of sync because:
    (a) applications are launched locally at different times, and
    (b) internal clocks may diverge over time.
The middleware assumes the maximum time among all peers the be the
``correct real time'', so that other peers must fast forward to catch up with
it.
Therefore, in order to determine the maximum time and synchronize the clocks,
the middleware proceeds as follows:
    (a) peers broadcast \code{SYNC} events periodically with their local
        times, and
    (b) if a peer is behind a received \code{SYNC}, it advances its frames
        proportionally faster to catch up in time.
%
\item \textbf{Peer Churn:}
Considering that we target peer-to-peer networks, it is important that the
middleware can handle arrival and departure of peers seamlessly.
When a peer leaves the network, nothing needs to be done.
The middleware just needs to ensure that a peer that joins the network receives
all events in order, which is trivial since they all hold an absolute
timestamp.
\end{enumerate}

 to ensure that all
peers (a) meet event deadlines, (b) advance in sync in real time, and (c) can
leave and join the network and remain symmetric.
%
For each of these goals, we measure (a) the recurrence of time travels, (b) the
real-time pace of peers, and (c) the correctness of unstable peers.

, respectively.

, such that
they validate goals (a), (b), and (c), respectively.

For each of these goals, we simulate different network scenarios varying the
(i) topology, (j) latency, (k) churn, and (k) frequency and (m) deadlines of
events.
For each scenario, we measure (x) the recurrence of time travels, (y) the
real-time pace of peers, and (z) the correctness of unstable peers, such that
they validate goals (a), (b), and (c), respectively.

- start with random deltas

@@

- use of space for snapshots
    - limit to go back?
    - super nodes? (when connecting, pass tick, may close if tick<last)
